Cluster Difference Imaging Photometric Survey. III. An Open Cluster Spread Across 400\,pc

### 2021-03-10 cluster_paper/ms.tex
update ms

The third and final approach we took for confirming the youth of the
halo population of \cn\ was an analysis of the Li\,\textsc{I}
6708\,\AA\ doublet.  The method has been reviewed by
\citet{soderblom_ages_2010}, and its connection to stellar rotation
has recently been surveyed by \citet{bouvier_lithium-rotation_2020}.
For \cn, two spectroscopic datasets  seemed particularly important:
Gaia-ESO \citep{randich_gaiaeso_2018} and GALAH DR3
\citep{buder_galah_2020}.  The target selection and results from each
survey were as follows.

Gaia-ESO selected {\it cluster candidates} to be observed with the
GIRAFFE and UVES spectrographs based on previously reported literature
members and publicly available optical and NIR photometry.  This
target selection approach included some stars in the spatial proximity
of previously known members.  Since the existence of the \cn\ halo was
not known at the time of target selection, very few ``halo'' stars are in
the sample.  For \cn, \citet{randich_gaiaeso_2018} ultimately
reported stellar parameters (including lithium equivalent widths and
metallicities) for 796 stars that they considered possible \cn\
members.  Cross-matching against our kinematic list of \nkinematic
candidate members by position and imposing a 0$\farcs$5 maximum
separation limit yields 492 kinematic members for which a Gaia-ESO
spectrum was acquired and stellar parameters were reported.  15 of
these (all with $(Bp-Rp)_0 > 2.0$) are spurious matches based on the
Gaia color and GES effective temperature, and we remove them.  This
yields 477 stars, of which 436 are in the core, and 41 are in the
halo.  The lop-sided ratio is primarily caused by the Gaia-ESO
selection function.
%FIXME VERIFY THAT THESE NUMBERS DON'T INCLUDE THEIR NANS...

@@

The GALAH DR3 target selection process is discussed in detail by
\citet{buder_galah_2020}.  The most relevant aspects for our project
are that the ``main'' survey targeted $12.0<V<14.0$ stars at
$\delta<+10^\circ$, provided the stars were at least ten degrees from
the galactic plane.  The survey is spatially
inhomogeneous\footnote{See the footprint at
\url{https://www.galah-survey.org/news/announcing-galah-dr3}}. Special
targeting for stars in the TESS southern continuous viewing zone, and
for known open cluster members was also performed.  We identified the
candidate \cn\ members for which spectra had been obtained by
searching the \texttt{GALAH\_DR3\_main\_allstar\_v1} catalog, after
excluding stars with the stellar parameter bit flags 1, 2, 3.  This
excludes spectra with unreliable broadening, low S/N, and unreliable
wavelength solutions (see Table~6 of \citealt{buder_galah_2020}).
Since our main focus is measuring equivalent widths for the
Li\,6708\,\AA doublet, these were the most relevant bit flags.  Of our
\nkinematic candidate \cn\ members, 107 had spectra in GALAH DR3.  51
were in the ``core''; 56 were in the ``halo''.  78 had ``finite''
lithium, i.e., no lithium flag set.

%FIXME FIXME FIXME FIXME
%FIXME FIXME FIXME FIXME

%
%/Users/luke/Dropbox/proj/earhart/results/lithium/kinematic_X_galah_dr3.csv
%
% https://docs.datacentral.org.au/galah/dr3/catalogue-data-access/
We downloaded\footnote{Via \url{datacentral.org.au/services/download},
using the \texttt{sobject\_id} identifiers.} the GALAH DR3 spectra for
all 107 entries.
We then measured the lithium equivalent widths using PROCESS Y.
We then concatenated the GALAH DR3 and Gaia-ESO results together.

>>>>

The third and final approach we took for confirming the youth of the
halo population of \cn\ was an analysis of the Li\,\textsc{I}
6708\,\AA\ doublet.  The method has been reviewed by
\citet{soderblom_ages_2010}, and its connection to stellar rotation
has recently been surveyed by \citet{bouvier_lithium-rotation_2020}.
For \cn, two spectroscopic datasets seemed particularly important:
Gaia-ESO \citep{gilmore_gaiaeso_2012} and GALAH
\citep{silva_galah_2015}.  At the time of analysis, Gaia-ESO DR4 and
GALAH DR3 were the most relevant, respectively \citep[{\it
e.g.},][]{randich_gaiaeso_2018,buder_galah_2020}.  The target
selection and results from each survey were as follows.

Gaia-ESO selected candidate \cn\ members to observe with the GIRAFFE
and UVES spectrographs based on previously reported literature members
and publicly available photometry.  Since the existence of the \cn\
halo was not known at the time of target selection, very few ``halo''
stars are in the sample.  For \cn, \citet{randich_gaiaeso_2018}
ultimately reported stellar parameters (including lithium equivalent
widths and metallicities) for 796 stars that they considered possible
\cn\ members.  Cross-matching against our kinematic list of
\nkinematic candidate members by position and imposing a 0$\farcs$5
maximum separation limit yields 492 kinematic members for which a
Gaia-ESO spectrum was acquired and stellar parameters were reported.
15 of these (all with $(Bp-Rp)_0 > 2.0$) are spurious matches based on
the Gaia color and GES effective temperature, and we remove them.
This yields 477 stars, of which 436 are in the core, and 41 are in the
halo.  The lop-sided ratio is due to the Gaia-ESO selection function.
We verified by directly querying the ESO archive that
\citet{randich_gaiaeso_2018} indeed included $>99\%$ of the available
spectra as part of their \cn\ sample, and so we opted to use their
results rather than repeating their analysis.

@@

The GALAH DR3 target selection is discussed in depth by
\citet{buder_galah_2020}.  The relevant aspects for our analysis
are that the ``main'' survey targeted $12<V<14$ stars at
$\delta<+10^\circ$, provided the stars were at least ten degrees from
the galactic plane.  The survey is spatially
inhomogeneous\footnote{See the footprint at
\url{https://www.galah-survey.org/news/announcing-galah-dr3}}. Special
targeting for stars in the TESS southern continuous viewing zone, and
for known open cluster members was also performed.  We identified the
candidate \cn\ members for which spectra had been obtained by
searching the \texttt{GALAH\_DR3\_main\_allstar\_v1} catalog, after
excluding stars with the stellar parameter bit flags 1, 2, 3.  This
excludes spectra with unreliable broadening, low S/N, and unreliable
wavelength solutions (see Table~6 of \citealt{buder_galah_2020}).
Since our main focus is measuring equivalent widths for the
Li\,6708\,\AA doublet, these were the most relevant bit flags.  Of our
\nkinematic candidate \cn\ members, 107 had spectra in GALAH DR3.  51
were in the ``core''; 56 were in the ``halo''.  78 had ``finite''
lithium, i.e., no lithium flag set.

%
%/Users/luke/Dropbox/proj/earhart/results/lithium/kinematic_X_galah_dr3.csv
%
% https://docs.datacentral.org.au/galah/dr3/catalogue-data-access/
We downloaded\footnote{Via \url{datacentral.org.au/services/download},
using the \texttt{sobject\_id} identifiers.} the GALAH DR3 spectra for
all 107 entries.  We then measured the lithium equivalent widths using
the AstroPy-affiliated \texttt{specutils} package
\citep{specutils_v1pt1}.

%FIXME TODO: put it into words
% circa ~line 1224 from ~/Dropbox/proj/cdips_followup/cdips_followup/spectools.py
Our procedure was as follow...

We then measured the lithium equivalent widths using PROCESS Y.
We then concatenated the GALAH DR3 and Gaia-ESO results together.
